Lyman-$\alpha$ photons through rotating outflows

### 2018-04-02 paper/paper.tex
2 typos

Nevertheless, an study of the combined effects of outflows and
rotation has not been presented in the literature.
Here we report on such a study. 
We investigate a simplified geometrical configuration corresponding to a
spherical gas cloud with symmetrical radial outflows and solid body
rotation. 
We base our modeling on a Monte-Carlo radiative transfer code.
Besides modeling the impact of joint rotation and outflows, we also
check to what extent the semi-analytical model presented by
\cite{Garavito14} an also be applied in our case.

@@

For each model setup we follow $10^5$ individual photons generated at
the center of the sphere at the \lya line's center as they propagate
through the volume and finally scape.
We store the final frequency and propagation direction for each photon
at its last scattering.

>>>>

Nevertheless, a study of the combined effects of outflows and
rotation has not been presented in the literature.
Here we report on such a study. 
We investigate a simplified geometrical configuration corresponding to a
spherical gas cloud with symmetrical radial outflows and solid body
rotation. 
We base our modeling on a Monte-Carlo radiative transfer code.
Besides modeling the impact of joint rotation and outflows, we also
check to what extent the semi-analytical model presented by
\cite{Garavito14} an also be applied in our case.

@@

For each model setup we follow $10^5$ individual photons generated at
the center of the sphere at the \lya line's center as they propagate
through the volume and finally escape.
We store the final frequency and propagation direction for each photon
at its last scattering.
